Urban Connectivity Dynamics: Analyzing Free Public WiFi Distribution in Toronto

### 2024-04-17 outputs/paper/paper.qmd
Add more detailed explanations for the model parts

### Model justification

@@

building_data |> 
  ggplot(aes(x = BuildingType, y = Number_of_free_wifi)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  labs(
    title = "The number of free Wifi in Toronto by building type",
    x = "Building Types",
    y = "Number of Free Public Wifi"
  )

@@

```{r}
#| label: fig-1
#| fig-cap: Linear regression model of the number of produced ASL words by the range of children's ages during their early developmental years.
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-2
#| fig-cap: Linear regression model of the number of produced ASL words by the range of children's ages during their early developmental years.
#| echo: false
#| warning: false

>>>>

## Model justification

@@

building_data |> 
  ggplot(aes(x = BuildingType, y = Number_of_free_wifi)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 90, hjust=1)) +
  labs(
    x = "Building Types",
    y = "Number of Free Public Wifi"
  )

@@

```{r}
#| label: fig-1
#| fig-cap: Linear regression model of the number of Free public wifi by the populations of all wards in Toronto.
#| echo: false
#| warning: false

@@

```{r}
#| label: fig-2
#| fig-cap: Linear regression model of the number of Free public wifi by the Average Income of all wards in Toronto.
#| echo: false
#| warning: false
